formula1

### 2020-06-10 inst/f1points.Rmd
more work (this one processes correctly)

>>>>

# more efficient ways

```{r,label=multiplemontecarlosetup, echo=FALSE, cache=FALSE}
top <- 11
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
#m <- maxp(ordertable2supp(as.ordertable(f2017)))

## Now work on synthetic dataset generation:
resampling_multiple <- function(m,f2017,pointslist){
    random_table <- rrank(n=ncol(f2017), p=m)
    rownames(random_table) <- colnames(f2017)
    ## "random_table" is a random table; now calculate lstar and pstar for
    ## likelihood ranks and points ranks respectively:

	goodnesses <- seq_along(pointslist)
	for(i in seq_along(pointslist)){
		p_star <- ordertable2points(as.ordertable(ranktable_to_ordertable(random_table)),pointslist[[i]])
		p_star <- sort(p_star,decreasing=TRUE)
		p_star[] <- seq_along(p_star)
		goodness <- sum(cumprod(names(p_star)==names(l_star)))
		goodnesses[i] <- goodness
		}
	return(goodnesses)
}
pointslist <- list(
	real = points_real,
	line = top:1,
	top1 = rep(1,1),
	top2 = rep(1,2),
	top3 = rep(1,3),
	top4 = rep(1,4),
	zipf = 1/seq_len(top),
	exp2 = 1/2^seq_along(top),	
	exp3 = 1/3^seq_along(top),	
	exp4 = 1/4^seq_along(top)
)
```

```{r,label=multiplemontecarloexecute, cache=TRUE,echo=TRUE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))
OO <- replicate(500+500,resampling_multiple(m,f2017,pointslist=pointslist))
```

```{r,label=multiplemontecarlotabulation}
M3 <- t(apply(OO,1,function(o){tabulate(o+1,nbins=12)}))
dimnames(M3) <- list(system=names(pointslist),correct=0:11)
M3
Mc <- t(apply(M3,1,cumsum))
Mc
```

and visuial:

```{r,label=plotcumulativeM,fig=TRUE}
matplot(t(Mc),type="b",lty=1,pch=16,col=rainbow(nrow(Mc)))
legend("bottomright",lty=1,pch=16,col=rainbow(nrow(Mc)),legend=letters[seq_len(nrow(Mc))])
plot(points_real)
grid()
```
